\documentclass{beamer}

\title{Word Sketch}
\subtitle{Skribbl using Elixir and Phoenix}
\date{11 Dec 2024}

\usetheme{Antibes}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}


\begin{frame}
    \frametitle{Team Members}
    \begin{itemize}
        \item Harish
        \item Pradeepaa M
        \item Sharon Prabhu
        \item Surya
        \item Yaswitha Boppana
    \end{itemize}
\end{frame}


\begin{frame}
    \frametitle{Learnings}
    \begin{itemize}
    \item Installation of a software in Linux by reading the documentation.
    \vspace{1 mm}
    \item Learning a language within a limited time (learning by doing).
    \vspace{1 mm}
    \item Planning and brainstorming with the team.
    \vspace{1 mm}
    \item Splitting work between team and team coordination.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Learnings}
    \begin{itemize}
        \item Elixir and Phoenix.
        \vspace{1 mm}
        \item Learning from mistakes/errors - Debugging.
        \vspace{1 mm}
        \item Perfection cannot be expected when you have just started learning a new skill, start with basics and build.
        \vspace{1 mm}
        \item Importance of git and documenting your learning.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Techstack - Backend}
    \begin{itemize}
        \item Elixir and Phoenix
        \vspace{1 mm}
        \item Phoenix LiveView
        \vspace{1 mm}
        \item Phoenix Channels
        \vspace{1 mm}
        \item Ecto: For handling data storage
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Techstack - FrontEnd \& DataBase}
    \begin{itemize}
        \item HTML5 Canvas
        \vspace{1 mm}
        \item JavaScript
        \vspace{1 mm}
        \item PostgreSQL
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Features}
    \begin{itemize}
        \item User Authentication
        \vspace{1 mm}
        \item Game Room Creation
        \vspace{1 mm}
        \item Word Assignment
        \vspace{1 mm}
        \item Real-Time Drawing
        \vspace{1 mm}
        \item Real-Time Guess Updates
        \vspace{1 mm}
        \item Points for Correct Guess
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{center}
       \large{Thank You}
    \end{center}
\end{frame}

\end{document}

